---
title: "In Class Work1"
author: "Sasha Uspenskaya"
date: "2024-01-29"
output:
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("/Users/sashauspenskaya/Desktop/Data Science/Data Science Labs")
```

```{r}
library(tidyverse) 
library(dplyr)
```

#1) Write a function that will find the sum of the natural log, the common log and a log of base 2 for any given positive number. Use your function to find answers for the first five even integers. Show all details and structure of your function. You should get five answers. The first two answers are 1.994177 and 3.988354

```{r}
logn<- function(x) {
  log(2*x)+log10(2*x)+log2(2*x)
}

logn(1:5)
```

#2) Use the if-else structure to print the statement "This is a big number" if the square of a value is greater than or equal to 100 and the following statement is printed if the square of the number is less than 100, "This is not a big number". Use and show values of assignment and if- else structures that will output both statements.


```{r}
x <- function(x) {
  if (x^2 > 100) {
    result <- "This is a big number"
  }
  else if (x^2 < 100) {
    result <- "This is not a big number"
  }
  return(result)
}

x(3)
x(20)
```

