---
title: "Lab 2"
author: "Alexandra Uspenskaya"
date: "2024-01-29"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(dplyr)
```

#1) Why is the vector shown an atomic vector? (Explain using two or three sentences)

V <- c("Bears", "Lions", "Dolphins", "Eagles", "Bengals") 
An Atomic Vector is homogeneous, meaning the items in the vector are all the same type. All items in the vector above are character strings.

# 2) Use and show R code that will extract "Dolphins" from the vector shown above.
```{r}
V <- c("Bears", "Lions", "Dolphins", "Eagles", "Bengals") 
V[3]
```

# 3) Use and show Rcode that will extract "Bears" , "Dolphins" and "Bengals" from the vector shown above.

```{r}
V[c(1,3,5)]
```
# 4) Use and show two Rcoding methods that will show all objects of the vector given above except "Bears".

```{r}
V[-1]
```

```{r}
V[c(2,3,4,5)]


```


# 5) Why is the vector given called a list? (Explain in two or three sentences) If the vector is a list, identify the type of each object in the list.
K <- list( x = 3:7, "never", 43, y = list(10,20,30))
We are storing elements of different types in the same vector. To this we create it using the list() function. 


# 6) Use and show R code that will give the length of the vector shown above.
```{r}
K <- list( x = 3:7, "never", 43, y = list(10,20,30))
length(K)
```

#7) Use and show R code that will output the fourth object in the vector shown above.
```{r}
K[4]
```
# 8) Use and show R code that will show all objects in the vector (list) given above. 

```{r}
K[c(1,2,3,4)]
```
#9)
```{r}
tribble(~x, ~y, ~w, ~z,
210, 300, 220, 180,
102, 100, 119, 187,
176, 175, 188, 173,
87, 95, 91, 94,
202, 210, 234, 218,
110, 122, 131, 128,
) -> dt
dt
```

# 9a) Use and show a map function to find the mean of each column of the dt data table


```{r}
mean(dt$x)
mean(dt$y)
mean(dt$w)
mean(dt$z)
```
#9b) Use and show a map function to find the standard deviation of each column of the dt data table.

```{r}
map_dbl(dt, sd)
```

# 9c) Use and show a map function that will calculate the square root of each value of each column of the data table dt
```{r}
map_df(dt, sqrt)
```

# 9d) Use R code to find the mean, max, 1st Quartile, 2nd Quartile, Median, and Mean for each column of the dt data table. (Hint: You do not have to use a map function)
```{r}
summary(dt$x)
summary(dt$y)
summary(dt$w)
summary(dt$z)
```




# 10)
```{r}
x <- list(26, 32, 45, 50, 65, 77, 82)
y <- list(30, 43, 50, 58, 62, 71, 88)
```

For the lists given above, show and use R code (a map function) to iteratively find:

## a) sums across the two vectors. (Use two methods)
```{r}
map_dbl(1:7, ~x[[.x]]+y[[.x]])

summ<- function(x,y)
  for (i in seq_along(x)){
    print(x[[i]]+y[[i]])
  }
summ(x,y)
```


##b) the calculation of the square of the x value minus the square root of the y value.

```{r}
map_dbl(1:7, ~sqrt(x[[.x]])-sqrt(y[[.x]]))
```


##c) the ratio of the common log of the x value to the natural log of the y value.

```{r}
map_dbl(1:7, ~log(x[[.x]])/log(y[[.x]]))
```
















