---
title: "Lab Week 4"
author: "Sasha Uspenskaya and Collin Coil"
date: "2024-02-12"
output:
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse) 
library(dplyr)
```

```{r}
x <- list(2, 4, 5, 9, 1)
y <- list(8, 7, 2, 8, 3)
z <- list(1, 8, 5, 4, 2)
```

# 1) 1) For the lists given above, show and use R code (a map function) to iteratively find the square of the sums across the vectors. 

```{r}
pmap_dbl(list(x,y,z), function(first, second, third) (first + second + third)^2)
```

```{r}
tribble( ~Student, ~Gender, ~Salary,
"John", "Male", 65000,
"Alice", "Female", 73000,
"Juan", "Male", 66000,
"Beth", "Female", 71500,
"Denise", "Female", 82000
) -> table
table
```
# 2) Using the data table above, use and show R code that will output a statement that is descriptive for all rows of the data table.

```{r}
table %>% 
  pmap_chr(~ str_glue("{..1} who is a {..2}, has a salary that is {..3} dollars per year."))
```

# 3) Write a nested loop that will produce a 5 by 5 matrix that whose matrix elements are sums of the corresponding columns and rows. Your code should produce the matrix below:

```{r}
z <- matrix( nrow = 5, ncol = 5)
for (m in 1:5) {
  for (n in 1:5) {
    z[m, n] <- (m + n)
  }
}
print(z)
```

# 4 ) Use for loop coding to produce the number sequence shown below: Note that the numbers 5 and 10 are missing

```{r}
x <- 1:20
for (val in x) {
  if (val == 5 | val==10){
    next
  }
  print(val)
}
```